Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-12-12 paper.tex
plural

To avoid side-channel attack (for example, based on
timing~\citep{bernstein:timing-attack-AES}) over software
implementations, this pipeline is implemented as a purely
combinational circuit. In particular, we are forbidden from performing
control-flow operations on secret data, leaving only
statically-bounded loops. We are also forbidden from performing memory
access based on the secret data, leaving only register spilling.

>>>>

To avoid side-channel attacks (for example, based on
timing~\citep{bernstein:timing-attack-AES}) over software
implementations, this pipeline is implemented as a purely
combinational circuit. In particular, we are forbidden from performing
control-flow operations on secret data, leaving only
statically-bounded loops. We are also forbidden from performing memory
access based on the secret data, leaving only register spilling.
